\documentclass[11pt, letterpaper]{article}
\usepackage[includehead, margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage[british]{babel}
\usepackage{sansmathfonts}
\usepackage{soul}
\usepackage{siunitx}
% \usepackage{textgreek}
\usepackage{mhchem}
\usepackage{modiagram}
\usepackage{tikzorbital}
\usepackage{chemfig}
\usepackage{xspace}
\newcommand{\degree}{\ensuremath{{}^{\circ}}\xspace}
\renewcommand{\familydefault}{\sfdefault}


\begin{document}

\fancypagestyle{plain}{
\fancyhf{}
\fancyhead[L]{CHEM 112L - M60 \\ Dr. Moulder \\TA: Xiaoyu Zhang}
\fancyhead[R]{H. Ryott Glayzer \\\:\\ 30 Jan 2024}
\fancyhead[C]{Lab Report \\ Handling Data \\ \:}
}


\title{Lab Report \\ \large Handling Data}
\author{H. Ryott Glayzer}
\date{\today}


\maketitle


\section*{Notice of ADA Accomodation}
I have an ADA accommodation to type out my pre-lab report when my disability flares up.
This document is a utilization of that accomodation.


\section{Post-Lab Questions}
\subsection{9.1}
\subsubsection{9.1.1}
I was able to make a reasonable hypothesis based lagely on the smell of the chemicals.

\subsubsection{9.1.2}
The smell was a physical property, and the flammability was chemical.

\subsubsection{9.1.3}
The flammability and temperature are intensive properties and the volume and mass were extensive properties.

\subsubsection{9.1.4}
Another qualitative observation that could be useful would be a relative pH test. Maybe some chemicals varied in pH,
and taking a relative pH test, comparing the differences rather than absolute pH's, would be qualitative.

\section{Conclusions}

This lab demonstrated the importance of qualitative and quantitative observations in chemistry.
I didn't learn much compared to what I learned in high school chemistry in this lab.
However, I had some issues getting the lab done after my lab partner left.


The lab also taught the importance of organizing data. 
One way this was done was with a spreadsheet software.
I use spreadsheet software in my daily work in the particle astrophysics lab.


































\end{document}

