\documentclass[10pt, letterpaper]{article}
\usepackage[includehead, margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage[british]{babel}
\usepackage{sansmathfonts}
\usepackage{soul}
\usepackage{color}
\usepackage{colortbl}
\usepackage{lewis}
\usepackage{siunitx}
\usepackage{textgreek}
\usepackage{mhchem}
\usepackage{modiagram}
\usepackage{tikzorbital}
\usepackage{chemfig}
\usepackage{xspace}
\definecolor{error}{rgb}{255,255,0}
\newcommand{\degree}{\ensuremath{{}^{\circ}}\xspace}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\fancypagestyle{plain}{
\fancyhf{}
\fancyhead[L]{CHEM 112 - M01 \\ Dr. Moulder}
\fancyhead[R]{H. Ryott Glayzer \\ 20 February 2024}
\fancyhead[C]{Assignment \\ \textit{Chapter 5: Advanced Theories of Bonding}}
}


\title{Chapter 5: Advanced Theories of Bonding}
\author{H. Ryott Glayzer}
\date{20 February 2024}


\maketitle


\section*{Notice of ADA Accommodation and Methods}
I have an ADA accommodation to do my assignment on paper.
This document is a utilization of that accommodation.
This assignment will utilize questions from the textbook,
\textit{Chemistry: Atoms First, 2e}, to practice the skills
and learning objectives for this class.

\section{Valence Bond Theory}

\subsection*{Q.1: Explain how $\sigma$ and $\pi$ bonds are similar and how they are different.}
$\sigma$ bonds are bonds that form in s-orbitals, while $\pi$ bonds form in p-orbitals.

\subsection*{Q.5: A friend tells you that \ce{N2} has three $\pi$ bonds due to the
overlap of the three \textit{p}-orbitals in each Nitrogen atom. Do you agree?}
\ce{N2} would have two $\pi$ bonds and a $\sigma$ bond.

\section{Hybrid Atomic Orbitals}

\subsection*{Q.9: Explain why a Carbon atom cannot form five bonds using $sp^{3}d$
hybrid orbitals.}
Carbon can only take four more valence shell electrons. 
$sp^{3}$ are what Carbon has since it con only form four bonds.

\subsection*{Q.13: Sulfuric acid is manufactured by the series of reactions:\\
\ce{S8(s) + 8O2(g) -> 8SO2(g)}\\
\ce{2SO2(g) + O2(g) -> 2SO3(g)}\\
\ce{SO3(g) + H2O(l) -> H2SO4(l)}\\
Draw the Lewis Structure, predict the molecular geometry by VSEPR,
and determine the hybridization of sulfur for the following:}

\subsubsection*{a. Circular \ce{S8} model}
\chemfig{\lewis{S}{.}{.}{}{}{.}{.}{}{}*8(-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-\lewis{S}{.}{.}{}{}{.}{.}{}{}-)}
Tetrahedral; Bent, $sp^{3}$

\subsubsection*{b. \ce{SO2} molecule}
Bent, $sp^{2}$
\chemfig{\lewis{O}{.}{.}{.}{.}{}{}{}{}~\lewis{S}{}{}{.}{.}{}{}{}{}-\lewis{O}{}{}{.}{.}{.}{.}{}{}}

\subsubsection*{c. \ce{SO3} molecule}
Trigonal Planar; $sp^{2}$
\chemfig{\lewis{O}{.}{.}{.}{.}{.}{.}{}{}-[:-90]S(=[:0]\lewis{O}{}{}{.}{.}{.}{.}{}{})-[:-90]\lewis{O}{.}{.}{}{}{.}{.}{.}{.}}


\subsubsection*{d. \ce{H2SO4} molecule}
Tetrahedral, $sp^{3}$
\chemfig{H-\lewis{O}{}{}{.}{.}{}{}{.}{.}-S(=[:90]\lewis{O}{.}{.}{}{}{.}{.}{}{})(=[:-90]\lewis{O}{.}{.}{}{}{.}{.}{}{})-\lewis{O}{}{}{.}{.}{}{}{.}{.}-H}

\subsection*{Q.17: Strike-anywhere matches contain a layer of \ce{KClO3} and a
layer of \ce{P4S3}.
The heat produced by the friction of striking the match causes these two compounds
to react vigorously, which sets fire to the wooden stem of the match.
\ce{KClO3} contains the \ce{ClO3-} ion.
\ce{P4S3} is an unusual molecule with the following skeletal structure:}

\chemfig{P?[a]*6(-P(-[:90]S?[b])-P?[a]-[,2]S-P?[b]-S-[,2])}

\subsubsection*{a. Write the Lewis structures for \ce{P4S3} and the \ce{ClO3-} ion.}

\chemfig{P?[a]*6(-P(-[:90]S?[b])-P?[a]-[,2]S-P?[b]-S-[,2])}
\quad
\chemleft[
\chemfig{O-[:30]Cl(-[:-90]O)-[:-30]O}
\chemright]$^{-}$
\subsubsection*{b. Describe the geometry about the P atoms, the S atom, and the Cl atom in these species}
P: Trigonal Pyramidal;
S:  Bent, two lone pairs;
Cl: Trigonal Pyramidal


\subsubsection*{c. Assign a hybridization to the P atoms, the S atom, and tho Cl atom in these species}
$sp^{3}$ for all


\subsubsection*{d. Determine the oxidization states and formal charge of the atoms in \ce{P4S3}
and the \ce{ClO3-} ion.}


\begin{center}
	\begin{tabular}{|c||c|c|c|c|}
		\hline
        Atom & P & S & Cl & O \\
		\hline \hline
        Oxidation States & +1 & $-1\frac{1}{2}$ & +5 & -2 \\
		\hline
        Formal Charge & 0 & 0 & +2 & -1 \\
	  \hline
     \end{tabular}
\end{center}


\section{Multiple Bonds}

\subsection*{Q.21: The bond energy of a C-C  single bond averages 347 kJ mol$^{-1}$;
that of a \chemfig{C~C} triple bond averages 839 kJ mol$^{-1}$.
Explain why the triple bond is not three times as strong as the single bond.}
A triple bond is made of of one $\sigma$ bond and two $\pi$ bonds.
A $\sigma$ bond is stronger than a $\pi$ bond.

\subsection*{Q.25: Identify the hybridization of the central atom in each of the following
molecules and ions that contain multiple bonds:}


\begin{center}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
        \ce{ClNO} & \ce{CS2} & \ce{Cl2CO} & \ce{Cl2SO} & \ce{SO2F2} & \ce{XeO2F2} & \ce{ClOF2+} \\
		\hline
        $sp^{2}$ & $sp$ & $sp^{2}$ & $sp^{3}$ & $sp^{3}$ & $sp^{3}d$ & $sp^{3}$ \\
		\hline
	\end{tabular}
\end{center}



\subsection*{Q.29: Draw the orbital diagram for carbon in \ce{CO2} showing how many carbon atom
electrons ore in each orbital.}

\begin{modiagram}[names]
   \atom[Orbitals in Carbon]{left}{%
    1s = {0; pair} ,
    2s = {1; pair} ,
    2p = {1.5; up, up }
 }

   \atom[Hybridized Carbon in \ce{CO2}]{right}{%
    1s = {0; up} ,
    2s = {1; up} ,
    2p = {1.5; up, up }
 }
\end{modiagram}



These are: (sp: up), (sp: up), (2p: up), (2p: up), but I can't figure out the \LaTeX for it

\section{Molecular Orbital Theory}

\subsection*{Q.33: Can a molecule with an odd number of electrons ever be diamagnetic?
Explain why or why not.}

No. 
An odd number of electrons will always be paramagnetic.

\subsection*{Q.37: Explain why an electron in the bonding molecular orbital in the \ce{H2}
molecule has a lower energy than an electron in the 1\textit{s} atomic orbital hydrogen atoms.}

The pairing of the two bonding electrons lowers the system's energy compared to a lone atom.




\\
\;
\\

\hline

\\
\;
\\

\section*{Grading}

\begin{center}
	\begin{tabular}{|c|c||c|}
		\hline
		\textbf{Points Possible} & \textbf{Points Earned} & \textbf{Score} \\
		\hline
		32 & _ & __/32 \\
		\hline
	\end{tabular}
\end{center}





\end{document}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                                 Copypasta                               %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Table for questions with multiple parts

% \begin{center}
% 	\begin{tabular}{|c|c|c|c|c|}
% 		\hline
% 		_ & _ & _ & _ & _ \\
% 		\hline
% 		_ & _ & _ & _ & _ \\
% 		\hline
% 	\end{tabular}
% \end{center}
