\documentclass[12pt, letterpaper]{article}

%
%Margin - 1 inch on all sides
%
\usepackage[letterpaper]{geometry}
\usepackage{kpfonts}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%
%Doublespacing
%
\usepackage{setspace}
\doublespacing%

%
%Rotating tables (e.g. sideways when too long)
%
\usepackage{rotating}


%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} 
\chead{} 
\rhead{Glayzer \thepage} 
\lfoot{} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{0pt} 
\setlength{\headheight}{14.5pt}
\renewcommand{\footrulewidth}{0pt} 
%To make sure we actually have header 0.5in away from top edge
%12pt is one-sixth of an inch. Subtract this from 0.5in to get headsep value
\setlength\headsep{0.333in}


%
%Begin document
%
\begin{document}
\begin{flushleft}

%%%%First page name, class, etc
H. Ryott Glayzer\\
Dr.\ Herrick\\
ENGL 101 MT1\\
10 May 2024\\


%%%%Title
\begin{center}
	\large Wanáǧi-Tȟačháŋu Máni Mitȟáŋ\\ 
	\scriptsize \textit{(My Little Sister Walks the Spirit Path)}
\end{center}


%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here




The stars were out that night as I lost myself in the grass, beating my chest and gnashing my teeth.
It’s interesting how those actions seem so odd when you read about them in the Bible,
but when shit hits the fan, it’s some primal instinct.
% As difficult as things had been leading up to this,
% things were going to be much more difficult going forward.
\vspace{5mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%    This was cut because I don't like it.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% I lay limp on the back seat of my friend’s truck,
% speeding down the highway at 75 miles an hour.
% My face is hot and wet with tears as I try to process what just happened.
% My sister is dead.
% Gone.
% I will never see her again, and somehow I have to accept that.
% I sit up and stare out the front windshield watching the lines on the road whisk
% by and try to forget my pain, try to push it down so it can’t hurt me.
% As warm tears stream down my face, I realize that would be a fruitless endeavor:
% I needed to face this head on and let myself feel my feelings.
% I collapse back into a heap on the seat, unable to control my bawling.
% In that moment, I knew my life would never be the same. 

% Back to before she died
I had just finished getting my new truck registered
at the county administration building.
% The truck was legally mine, but in all reality it is my wife’s truck.
% I hadn’t driven there, though.
% I biked there, like I do most places.
% The line was long now and squeezing past the lines of tired-eyed people
% who definitely did not want to be there was a task in and of itself.
% Nevertheless, I squished past the last dreary-eyed person and hustled out the door.
My mom and grandma were in the parking lot,
they wanted to meet with me before they took my sister to the hospital.
She had been sick for a few days and wasn’t getting better.
Her doctor had tested her for strep, mono, and a battery of other sicknesses,
but they all had come back negative.
She had a plethora of disabilities that worked together to make
her immune system weak, so any illness was scary.
%%% Maybe now I can drop the immune comp part
% I needed to use my mom’s car to go get my wife’s truck,
% so she dropped off her car with me before taking my sister to the hospital.
% When I got to them, my mom and grandma were both crying and looked really worried.
% My sister was immune compromised and they were worried because she was just so sick.
She had been sick for a few days and it just kept getting worse.
I was confident, however, that my sister was just fine and that she would pull
through this like she pulled through everything else.
This little girl had gone through 20 surgeries in her twelve years of life,
I was sure she could handle a little flu.
I think my confidence was a coping mechanism for my worries, though.
I was always worried about her.
This little girl was the center of all of our lives.
I opened the door to my grandma’s car where my sister was sitting, half awake.
I looked at her little face and told her how much I loved her, that
she would be okay and that we’re all rooting for her.
I took her up in my arms and gave her a big kiss on the forehead.
At the urging of my mom and grandma,
I let go of her because they needed to go to the hospital.
Looking back, I am glad that I took the time to tell her that,
and to give her a hug and a kiss.
That was the last time I saw my sister. 
\vspace{5mm}


% That night, I went home with my mom’s car and my wife went home with her new truck.
% We had been living in our bus, but with Kymberlyn in the hospital,
% my mom wanted us to watch the pets.
% That was fine by me, my mom’s house is much closer to Mines than where the bus was parked,
% and it has running water.
% So we went, packed up our four cats and our stuff and moved into my mom’s house.
% We thought we would be there for a week at most.


After my sister went to the ER, she took a turn for the worse.
Her liver and kidneys were failing and she was in a lot of pain.
It didn't take long for her to start being sassy to the nurses, 
who decided to give her a downer to `calm her down
because she was cussing too much.
Suddenly, she lost her vision.
The medicine the nurse gave her to shut her up had damaged her liver even more,
to the point that she went blind and mostly unresponsive.
It was soon that she started showing symptoms of pneumonia as well.
Monument Health decided, after damaging her liver and calling my mother
a bad parent for crying too much to comfort her child, that they couldn't 
provide the level of specialist emergency care that Kymberlyn needed and 
called for the life flight to take her to a specialist hospital in Omaha, NE\@.
\vspace{5mm}


I was devastated.
Because I was the oldest and most responsible sibling,
I had to stay behind and watch my younger brother and the pets.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% I had  to take my grandpa to the ER and fell asleep revising %%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over the next four days,
her health only seemed to get worse.
She was put on life support and the rest of the family
went down to Omaha to be there for her.
% My brain is too sad for this this is really hard.
% I really want this to be perfect for Kymberlyn
I wanted to stop everything in my life and go to Omaha,
but I couldn't, and that hurt.
I just had to keep going.
I had to take care of the dogs.
I had to play a show in Aberdeen.
I had to work through the worry and the grief and all of the things
that wounded my heart.
% čhaŋtíyapȟamič'iya čhaŋtéšiča: 
% the dictionary says "to allow oneself to become emotional" -> "sadness"
% but that seems like a really clinical translation for a word that carries
% such feeling. Maybe "I fell into a worrisome sorrow that wounded my heart"
I knew that Kymberlyn would want me to keep going, so I did.
\vspace{5mm}
% It was midterms and I was neck-deep in studying for exams.
% But I was worried.
% It seemed like every couple minutes something else would go horribly wrong.
% Her liver and kidneys were failing and she was in and out of consciousness.
% That same night, she was life-flighted out to
% Omaha, NE because she just wasn’t getting better.
% She was eventually put on life support and even went blind.
% Nothing seemed to help.
% The hospital told us it was Influenza B
% (We later found out it was influenza A)
% and that they didn’t know why her reaction was so bad.
% Later we found out that Monument ER had given her a downer
% because she was being mean to the nurses and her reaction
% to that medicine is what caused everything to get so much worse so fast.
% She held on strong over the weekend,
% while the hospital in Omaha tried everything they could to save her.
% I had a small tour planned for spring break with my band.
% With Kymberlyn as my courage, I decided to play two shows,
% one in Aberdeen SD and the other in Rapid City SD\@.
% All throughout the Aberdeen show, Kymberlyn seemed to be getting a little bit better.
% She started on ECMO, a treatment like dialysis, and it seemed to be working.
% The doctors told us that she had less than a 50\% chance of surviving that treatment.
% Sadly, they were right.








After playing the show in Aberdeen,
I was getting ready to lie down to sleep at a friend's house
when I got a call from my grandma.
She was bawling so hard I could barely understand her.
My heart sank in my chest.
% Dialogue
``We have to take her off life support.\@''
I could barely understand my grandma through the tears.
``They said she has a brain bleed and there's nothing we can do.\@''
% It was the call I was dreading, the call I wish I could have never gotten.
% She said that Kymberlyn had developed a brain bleed
% and that they were going to have to take her off of life support.
I cried uncontrollably.
My tears were like raindrops in a downpour.
I couldn’t fathom this happening.
At that moment, my sorrow was so great
that I went numb to my bodily sensations.
I floated out of the basement of the house
we were crashing in on a cloud of pain and confusion.
Each second that passed felt like it was scarring my mind.
I see the pity in the faces of each person I pass and I hate it.
I fly out the door with the last of my strength. 
As soon as my bare feet touch the grass,
I collapsed into a writhing ball of messy, complicated emotions.
\vspace{5mm}

``Why? Why God? Tȟuŋkášila, why?\@''
% onto the lawn and collapsed.
I pleaded with God as I beat the ground with my fists,
asking why He would do this, why He would cut her life so short.
I asked him to take me, the sinner, the one who has done so many horrible,
horrible things, instead of taking this sweet, innocent young girl.
As I drowned in great sorrow, 
my teary eyes looked to the sky, feeling lost.
I could see Wanáǧi-Tȟačháŋu, the Spirit Path,
and knew that soon my sister would walk it.
She would be safe and wouldn't be in pain.
Never again would she have to struggle up an
incline or over a bump in a wheelchair.
Her arms wouldn't dislocate every day anymore.
These things bring me some comfort now, 
but in that moment of great change,
I have to admit it still hurt. 
Maybe that makes me a monster,
but I think it just makes me human.
\vspace{5mm}


% The stars were out that night as I lost myself in the grass,
% beating my chest and gnashing my teeth.
% It’s interesting how those actions seem so odd when you read about them in the Bible,
% but when shit hits the fan, it’s some sort of primal instinct.



As I lay crumpled on the ground,
the world kept going around me.
My bandmates gathered the things
that I had left haphazardly in the basement.
They said we were going to try to speed down to Omaha
so I could see my sister before she passed.
The next thing I remember, we were flying down the 
interstate toward Omaha when my mom called me.
``You aren't going to make it down here in time,\@''
she said, bawling.
% My friends were with me, helping me get everything ready and get going.
% We thought we had time to get down to Omaha so
% I could see my sister one last time before she passed.
% We started rushing down there as fast as possible in the truck.
% Not even ten miles out of town, I get a video call from my mom.
% It’s too late.
% They had to take her off now.
``I'm gonna get you on video call so you can say goodbye to her.\@''
The truck had stopped and by this time I was outside on the side of the road.
My mom set up a video call with my wife, who was still at home, and me.
On the phone, I saw my sister.
She was hooked up to a dozen machines and
her face was so swollen I could barely recognize her.
She'd gone through so, so much for a girl her age and
she'd taught us all how to love in a way we never loved before.
That night, I got to see her face one last time and tell her how much
I loved her and how much I cared about her and how sorry
I was for being a mean older sibling.
I wept uncontrollably as I told her how I wished I spent more time with her
and how I regret being a bitch to her and how she really
was a big reason for me to keep on with a positive life.
Without her and my mother, I don’t think I would still be sober.
% We had pulled over at this point and I was in the ditch,
% bawling with my sister on the phone.
After what will always feel like not enough time,
she had to go.
I didn’t want to hang up.
I didn’t want to say goodbye.
I don’t think anyone ever does.
But I had to.
% I conference called in my wife, who was still at home, taking care of the animals.
% She wept and wept and wept and wept.
% After what felt like ages, my mom said they needed to go.
I collapsed again, under the bright starry sky in the middle of the highway.
I wished I could have been there, but my mom reminded me that my
sister would have been so grateful that I stayed behind to watch her puppies.
% In the meantime, my friend Ti had grabbed my gun and holster and put it in the trailer.
When I got back in the truck, 
everyone was crying.
Kymberlyn meant the world to all of us. 
\vspace{5mm}


At that moment, hundreds of miles away from where I was,
my sister took her last breath surrounded by her closest family
(save me and my wife) while our mom sang a lullaby to her.
My mom still rocks her ashes to sleep and sings that song some nights,
while I weep rooms away.
Our lives will never be the same.


% This is such a difficult story to write.




\end{flushleft}
\end{document}